From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-22 paper.tex
Minor formatting
Commented out the 'gaze-shift' part for now

\subsubsection{Relevance of Head Pose Estimation for Attention Tracking}
\label{sec:fromFaceTo}

@@

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. For each subject, the with-me-ness level is reported over the whole interaction, either based on the ground-truth (\ie \emph{ground-truth with-me-ness}), or based on the focus of attention measured by the robot.}
    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg. & SD \\
        \midrule
        $\mathcal{W}_{g.truth}$ & 92.6 & 88.8  & 95.8 & 93.1 & 96.5 & 89.6 & 92.7 & 3.1 \\ 
        $\mathcal{W}_{robot}$ & 89.6 & 84.4 & 86.6 & 72.8 & 81.9 & 79.7 & 82.5 & 5.4 \\
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}

@@

If we consider the case shown in section \ref{sec:fromFaceTo}, evaluating the
subject's progression together with the time on task may be an indicator of
engagement: If the subject answers so quickly with respect to the previous
attempts with a poorer handwriting may be the case she is not engaged anymore.
In such hypothetical case an activity switch can be easily implemented in a
robot architecture. It confirms the findings reported in \cite{anzalone} where
time response to event is proposed to account quality of interaction.

However, a high amount of gaze shift (figure \ref{fig:gazeR}) towards the
demonstration provided can reveal that the challenge is too big or no gaze, the
exactly the opposite. In this case, the robot response can be adapted to the
situation. Similar, but least relevant results are obtained using the
correctness (figure \ref{fig:errorR}) of the child's feedback after each
attempt.

\begin{figure}
  \centering
  \begin{tabular}{@{}c@{}}
    \includegraphics[width=.7\linewidth,height=100pt]{gazeR} \\
    \small (a) Occurrences of a gaze shift.
  \end{tabular}\label{fig:gazeR}

  \vspace{\floatsep}

  \begin{tabular}{@{}c@{}}
    \includegraphics[width=.7\linewidth,height=100pt]{errorR} \\
    \small (b) Word correctness.
  \end{tabular}\label{fig:errorR}

  \caption{ \small Linear regression of all subject attempts against the gaze
  shift tablet-model (a) and the correctness as the average euclidean distance
  of each letter in its corresponding eigenspace with respect to a reference
  letter (b). The gray region defines the confidence interval.}

\end{figure}

This information can be used to estimate the child's state during the
interaction. For instance, if we consider that a low level of engagement is
produced by extremely high or low demanding situations, it is possible to assess
the engagement level during the interaction based on gaze shift and word
correctness.

@@

During the case study, results show that it is possible to distinguish between
long and short feedback episodes based on the gaze shift and depending on the
previous attempts performed by the subject. As a result, gaze-shift together
with the number of attempts becomes a reliable indicator candidate in the
assessment of the engagement during the activity.

Additionally, both the gaze shift and the correctness of the feedback seem to be
strictly correlated with the learning gain during the activity as they go in
decrement after each attempt provided by the subjects. Despite the fact that
these results are encouraging, there is a need of validation with a greater
amount of subjects.

>>>>

@@

\begin{table}[h!]
    \centering
    \caption{\textbf{Levels of with-me-ness}. For each subject, the with-me-ness
    level is reported over the whole interaction, either based on the
    ground-truth (\ie \emph{ground-truth with-me-ness}), or based on the focus of
    attention measured by the robot.}

    \begin{tabular}{p{1cm}cccccccc}
        \toprule
        Subject & 1 & 2 & 3 & 4 & 5 & 6 & Avg. & SD \\
        \midrule
        $\mathcal{W}_{g.truth}$ & 92.6 & 88.8  & 95.8 & 93.1 & 96.5 & 89.6 & 92.7 & 3.1 \\ 
        $\mathcal{W}_{robot}$ & 89.6 & 84.4 & 86.6 & 72.8 & 81.9 & 79.7 & 82.5 & 5.4 \\
        \bottomrule
    \end{tabular}
    \label{tab:results-with-me-ness}
\end{table}

@@

If we consider the case shown in section \ref{sec:fromFaceTo}, evaluating the
subject's progression together with the time on task may be an indicator of
engagement: If the subject answers so quickly with respect to the previous
attempts with a poorer handwriting may be the case she is not engaged anymore.
In such hypothetical case an activity switch can be easily implemented in a
robot architecture. It confirms the findings reported in \cite{anzalone} where
time response to event is proposed to account quality of interaction. 
%
%However, a high amount of gaze shift (figure \ref{fig:gazeR}) towards the
%demonstration provided can reveal that the challenge is too big or no gaze, the
%exactly the opposite. In this case, the robot response can be adapted to the
%situation. Similar, but least relevant results are obtained using the
%correctness (figure \ref{fig:errorR}) of the child's feedback after each
%attempt. 
%
%\begin{figure}
%  \centering
%  \begin{tabular}{@{}c@{}}
%    \includegraphics[width=.7\linewidth,height=100pt]{gazeR} \\
%    \small (a) Occurrences of a gaze shift.
%  \end{tabular}\label{fig:gazeR}
%
%  \vspace{\floatsep}
%
%  \begin{tabular}{@{}c@{}}
%    \includegraphics[width=.7\linewidth,height=100pt]{errorR} \\
%    \small (b) Word correctness.
%  \end{tabular}\label{fig:errorR}
%
%  \caption{ \small Linear regression of all subject attempts against the gaze
%  shift tablet-model (a) and the correctness as the average euclidean distance
%  of each letter in its corresponding eigenspace with respect to a reference
%  letter (b). The gray region defines the confidence interval.}
%  
%\end{figure}
%
%
%This information can be used to estimate the child's state during the
%interaction. For instance, if we consider that a low level of engagement is
%produced by extremely high or low demanding situations, it is possible to assess
%the engagement level during the interaction based on gaze shift and word
%correctness.

@@

%During the case study, results show that it is possible to distinguish between
%long and short feedback episodes based on the gaze shift and depending on the
%previous attempts performed by the subject. As a result, gaze-shift together
%with the number of attempts becomes a reliable indicator candidate in the
%assessment of the engagement during the activity.
%
%Additionally, both the gaze shift and the correctness of the feedback seem to be
%strictly correlated with the learning gain during the activity as they go in
%decrement after each attempt provided by the subjects. Despite the fact that
%these results are encouraging, there is a need of validation with a greater
%amount of subjects.
